ストループ課題

### 2021-05-07 materials/jsPsych/stroop/stroop_p3.Rmd
update

/*刺激の設定*/
var stimuli = [
  {
    stimulus: "<p style='color:red;font-size:60pt;'>赤</p>",
    data: { no:'1', stim_type: 'congruent', correct_key_press: '90'}
  },
  {
    stimulus: "<p style='color:green;font-size:60pt;'>赤</p>",
    data: { no:'2', stim_type: 'incongruent', correct_key_press: '78'}
  },
  {
    stimulus: "<p style='color:yellow;font-size:60pt;'>赤</p>",
    data: { no:'3', stim_type: 'incongruent', correct_key_press: '77'}
  },
  {
    stimulus: "<p style='color:blue;font-size:60pt;'>赤</p>",
    data: { no:'4', stim_type: 'incongruent', correct_key_press: '88'}
  },
  {
    stimulus: "<p style='color:red;font-size:60pt;'>緑</p>",
    data: { no:'5', stim_type: 'congruent', correct_key_press: '90'}
  },
  {
    stimulus: "<p style='color:green;font-size:60pt;'>緑</p>",
    data: { no:'6', stim_type: 'incongruent', correct_key_press: '78'}
  },
  {
    stimulus: "<p style='color:yellow;font-size:60pt;'>緑</p>",
    data: { no:'7', stim_type: 'incongruent', correct_key_press: '77'}
  },
  {
    stimulus: "<p style='color:blue;font-size:60pt;'>緑</p>",
    data: { no:'8', stim_type: 'incongruent', correct_key_press: '88'}
  },
  {
    stimulus: "<p style='color:red;font-size:60pt;'>黄</p>",
    data: { no:'9', stim_type: 'congruent', correct_key_press: '90'}
  },
  {
    stimulus: "<p style='color:green;font-size:60pt;'>黄</p>",
    data: { no:'10', stim_type: 'incongruent', correct_key_press: '78'}
  },
  {
    stimulus: "<p style='color:yellow;font-size:60pt;'>黄</p>",
    data: { no:'11', stim_type: 'incongruent', correct_key_press: '77'}
  },
  {
    stimulus: "<p style='color:blue;font-size:60pt;'>黄</p>",
    data: { no:'12', stim_type: 'incongruent', correct_key_press: '88'}
  },
  {
    stimulus: "<p style='color:red;font-size:60pt;'>青</p>",
    data: { no:'13', stim_type: 'congruent', correct_key_press: '90'}
  },
  {
    stimulus: "<p style='color:green;font-size:60pt;'>青</p>",
    data: { no:'14', stim_type: 'incongruent', correct_key_press: '78'}
  },
  {
    stimulus: "<p style='color:yellow;font-size:60pt;'>青</p>",
    data: { no:'15', stim_type: 'incongruent', correct_key_press: '77'}
  },
  {
    stimulus: "<p style='color:blue;font-size:60pt;'>青</p>",
    data: { no:'16', stim_type: 'incongruent', correct_key_press: '88'}
  }
];

/*ストループ課題*/
var stroop = {
  timeline: [{
    type: "html-keyboard-response",
    choices: ["z","x","n","m"],
    trial_duration: 2000,
    response_ends_trial: true,
    stimulus: jsPsych.timelineVariable('stimulus'),
    prompt: '赤色ならz,  青色ならx,  緑色ならn,  黄色ならm',
    data: jsPsych.timelineVariable('data'),
    on_finish: function(data){
      var correct = 0;
      if(data.correct_key_press == data.key_press){
        correct = 1;
      } 
      data.correct = correct;
    },
    post_trial_gap: function() {
        return Math.floor(Math.random() * 1500) + 500;
    }
  }],
  timeline_variables: stimuli,
  sample: {type: 'fixed-repetitions',size: 2}
};

>>>>

/*刺激の設定*/
var stimuli = [
  {
    stimulus: "<p style='color:red;font-size:60pt;'>赤</p>",
    data: { no:'1', stim_type: 'congruent', correct_key_press: 'z'}
  },
  {
    stimulus: "<p style='color:green;font-size:60pt;'>赤</p>",
    data: { no:'2', stim_type: 'incongruent', correct_key_press: 'n'}
  },
  {
    stimulus: "<p style='color:yellow;font-size:60pt;'>赤</p>",
    data: { no:'3', stim_type: 'incongruent', correct_key_press: 'm'}
  },
  {
    stimulus: "<p style='color:blue;font-size:60pt;'>赤</p>",
    data: { no:'4', stim_type: 'incongruent', correct_key_press: 'x'}
  },
  {
    stimulus: "<p style='color:red;font-size:60pt;'>緑</p>",
    data: { no:'5', stim_type: 'congruent', correct_key_press: 'z'}
  },
  {
    stimulus: "<p style='color:green;font-size:60pt;'>緑</p>",
    data: { no:'6', stim_type: 'incongruent', correct_key_press: 'n'}
  },
  {
    stimulus: "<p style='color:yellow;font-size:60pt;'>緑</p>",
    data: { no:'7', stim_type: 'incongruent', correct_key_press: 'm'}
  },
  {
    stimulus: "<p style='color:blue;font-size:60pt;'>緑</p>",
    data: { no:'8', stim_type: 'incongruent', correct_key_press: 'x'}
  },
  {
    stimulus: "<p style='color:red;font-size:60pt;'>黄</p>",
    data: { no:'9', stim_type: 'congruent', correct_key_press: 'z'}
  },
  {
    stimulus: "<p style='color:green;font-size:60pt;'>黄</p>",
    data: { no:'10', stim_type: 'incongruent', correct_key_press: 'n'}
  },
  {
    stimulus: "<p style='color:yellow;font-size:60pt;'>黄</p>",
    data: { no:'11', stim_type: 'incongruent', correct_key_press: 'm'}
  },
  {
    stimulus: "<p style='color:blue;font-size:60pt;'>黄</p>",
    data: { no:'12', stim_type: 'incongruent', correct_key_press: 'x'}
  },
  {
    stimulus: "<p style='color:red;font-size:60pt;'>青</p>",
    data: { no:'13', stim_type: 'congruent', correct_key_press: 'z'}
  },
  {
    stimulus: "<p style='color:green;font-size:60pt;'>青</p>",
    data: { no:'14', stim_type: 'incongruent', correct_key_press: 'n'}
  },
  {
    stimulus: "<p style='color:yellow;font-size:60pt;'>青</p>",
    data: { no:'15', stim_type: 'incongruent', correct_key_press: 'm'}
  },
  {
    stimulus: "<p style='color:blue;font-size:60pt;'>青</p>",
    data: { no:'16', stim_type: 'incongruent', correct_key_press: 'x'}
  }
];

/*ストループ課題*/
var stroop = {
  timeline: [{
    type: "html-keyboard-response",
    choices: ["z","x","n","m"],
    trial_duration: 2000,
    response_ends_trial: true,
    stimulus: jsPsych.timelineVariable('stimulus'),
    prompt: '赤色ならz,  青色ならx,  緑色ならn,  黄色ならm',
    data: jsPsych.timelineVariable('data'),
    on_finish: function(data){
      var correct = 0;
      if(data.correct_key_press == data.response){
        correct = 1;
      } 
      data.correct = correct;
    },
    post_trial_gap: function() {
        return Math.floor(Math.random() * 1500) + 500;
    }
  }],
  timeline_variables: stimuli,
  sample: {type: 'fixed-repetitions',size: 2}
};
